### 2023-02-10 article.tex
Copy file

For code to be extensive enough to reproduce an existing experiment,
it should be distributed in standard ways \cite{peng2006reproducible}.
The standard way to publish code is to use a code hosting website.
There are multiple code hosting websites, 
with GitHub being the most popular one \cite{cosentino2017systematic}.
GitHub is a website where users can create dedicated pages (called 'repositories')
to upload code and interact with it.
The use of such code hosting websites
has increased strongly \cite{russell2018large},
accommodates collaboration \cite{perez2016ten}
and improves transparency \cite{gorgolewski2016practical}.
See \cite{cosentino2017systematic} for an extensive overview of
research conducted on GitHub.

@@

In software development, 
changes are common and should be embraced \cite{beck2000extreme}.
When a scientist intends to reuse code by extending its functionality,
first the code will be assessed,
after which the code may be actually extended.

Code is just 'another kind of data' and should be designed 
as such, for example, by using tools to work on it \cite{wilson2022twelve}.

A first example is to use a tool to enforce a coding style 
(e.g. the Tidyverse style guide \cite{wickham2019advanced} for R,
or PEP 8 \cite{van2001pep} for Python).
Following a consistent coding style improves software quality \cite{fang2001}.

A second example is to use a tool to enforce a low cyclomatic complexity.
The cyclomatic complexity is approximately defined 
as the number of independent paths that
the code can be executed. 
For example, code that has only one \verb|if| statement
has a cyclomatic complexity of 2, as the condition within the \verb|if|
statement can be true or false,
resulting in the body of the \verb|if| statement being either
exectuted or ignored.
The cyclomatic complexity correlates with code complexity,
where more complex code is likelier to contain or give rise to bugs 
\cite{abd2018calculating,chen2019empirical,zimmermann2008predicting}

@@

Coding errors are extremely common 
and contribute to the reproducibility crisis in science \cite{vable2021code}.

%.
%. How to make more published research true
%. NIH plans to enhance reproducibility
%. The replication crisis in epidemiology: snowball, snow job, or winter solstice?
%. The harm done to reproducibility by the culture of null hypothesis significance testing

@@

Testing, in general, is an important mechanism to ensure
the correctness of code (an interesting example is \cite{rahman2020exploratory}
showing bugs in scientific software on the COVID-19 pandemic:
it recommends more testing).
The percentage of (lines of) code tested is called the code coverage.
Code coverage correlates with code quality \cite{horgan1994,del1995correlation}. 
The non-profit organisation rOpenSci \cite{ram2018community},
which peer-reviews code,
has made it a prerequisite to have a code coverage of 100\%.
Also here, CI opens up the possibility to informally annotate the
code coverage. 
For example, build badges
\iffalse
(e.g. as shown in Figure \ref{fig:badge_codecov})
\fi
are visual indications on a website that can, among others,
show a certain R package's code has a 100\% code coverage.

@@

Code hosting websites such as GitHub help developers to follow
best practices. One of these is to add a software license \cite{jimenez2017four},
so that it is clear that the software can be reused.
About one in three of 56 Science magazine corresponding authors 
that shared their code via a URL or email
do not supply a software license \cite{stodden2018empirical}.

@@

@@

Preserving code by uploading it to a code hosting webite
has many advantages.

@@

Code is harder to preserve than an English text
and preserving code is rarely done \cite{barnes2010publish}.
Although code is the primary actor in computational experiments,
there is no incentive to submit code alongside a publication.
Most academic journal do not require authors to submit their code,
nor is the submitted code peer reviewed, 
rOpenSci \cite{ram2018community} being the pleasant exception.

>>>>

For code to be extensive enough to reproduce an existing experiment,
it should be distributed in standard ways \cite{peng2006reproducible}
(see section \ref{sec:code-availability}
for the general availability of code).
The standard way to publish code is to use a code hosting website.
There are multiple code hosting websites, 
with GitHub being the most popular one \cite{cosentino2017systematic}.
GitHub is a website where users can create dedicated pages (called 'repositories')
to upload code and interact with it.
The use of such code hosting websites
has increased strongly \cite{russell2018large},
accommodates collaboration \cite{perez2016ten}
and improves transparency \cite{gorgolewski2016practical}.
See \cite{cosentino2017systematic} for an extensive overview of
research conducted on GitHub.

@@

In software development, 
changes are common and should be embraced \cite{beck2000extreme}.

@@

Coding errors are extremely common 
and contribute to the reproducibility crisis in science \cite{vable2021code}.
Testing, in general, is an important mechanism to ensure
the correctness of code (an interesting example is \cite{rahman2020exploratory}
showing bugs in scientific software on the COVID-19 pandemic).

The percentage of (lines of) code tested is called the code coverage.
Code coverage correlates with code quality \cite{horgan1994,del1995correlation}. 
The non-profit organisation rOpenSci \cite{ram2018community},
which peer-reviews code,
has made it a prerequisite to have a code coverage of 100\%.
Also here, CI opens up the possibility to informally annotate the
code coverage. 
For example, build badges
\iffalse
(e.g. as shown in Figure \ref{fig:badge_codecov})
\fi
are visual indications on a website that can, among others,
show a certain R package's code has a 100\% code coverage.

@@

@@

Code hosting websites such as GitHub help developers to follow
best practices. One of these is to add a software license \cite{jimenez2017four},
so that it is clear that the software can be reused.
About two-thirds of 56 Science magazine corresponding authors 
that shared their code supply a software license \cite{stodden2018empirical}.

@@

% \paragraph{Ideal paradata}

For paradata to be useful, it has to be computer-friendly, yet 
'the best paradata does not necessarily look like 'data' at all for its
human users' \cite{huvila2022improving}.
There are features of code that humans find useful,
without directly being able to measure these.
In the end, code is just 'another kind of data' and should be designed 
as such, for example, by using tools to work on it \cite{wilson2022twelve}.

A first example is to use a tool to enforce a coding style 
(e.g. the Tidyverse style guide \cite{wickham2019advanced} for R,
or PEP 8 \cite{van2001pep} for Python),
as following a consistent coding style improves software quality \cite{fang2001}.

A second example is to use a tool to enforce a low cyclomatic complexity.
The cyclomatic complexity is approximately defined 
as the number of independent paths that
the code can be executed. 
For example, code that has only one \verb|if| statement
has a cyclomatic complexity of 2, as the condition within the \verb|if|
statement can be true or false,
resulting in the body of the \verb|if| statement being either
executed or ignored.
The cyclomatic complexity correlates with code complexity,
where more complex code is likelier to contain or give rise to bugs 
\cite{abd2018calculating,chen2019empirical,zimmermann2008predicting}.

Such tools combine great with CI services.

@@

Preserving code by uploading it to a code hosting webite
has many advantages.
Code is harder to preserve than an English text
and preserving code is rarely done \cite{barnes2010publish}.
Although code is the primary actor in computational experiments,
there is no incentive to submit code alongside a publication.
Most academic journal do not require authors to submit their code,
nor is the submitted code peer reviewed, 
rOpenSci \cite{ram2018community} being the pleasant exception.

@@
